Historical aerial surveys map long-term changes of forest cover and structure in the central Congo Basin

### 2020-02-06 manuscript/appendix.Rmd
AGC uncertainty + manuscript tweaks

>>>>

```{r echo = FALSE, eval = TRUE}
agc <- psp %>%
  group_by(type) %>%
  summarize(mean_agc = mean(above.ground.C.stock..Mg.C.ha.1.),
            sd_agc = sd(above.ground.C.stock..Mg.C.ha.1.),
            mean_sd = mean(stem.density..ha.1.),
            sd_sd = sd(stem.density..ha.1.),
            mean_ba = mean(basal.area....m2.ha.1.),
            sd_ba = sd(basal.area....m2.ha.1.),
            n = length(above.ground.C.stock..Mg.C.ha.1.))

mn_agc <- ifelse(!is.na(agc$sd_agc),
                paste(round(agc$mean_agc,2), round(agc$sd_agc,2), sep = " $\\pm$ "),
                round(agc$mean_agc,2))

mn_sd <- ifelse(!is.na(agc$sd_sd),
                paste(round(agc$mean_sd,2), round(agc$sd_sd,2), sep = " $\\pm$ "),
                round(agc$mean_sd,2))

mn_ba <- ifelse(!is.na(agc$sd_ba),
                paste(round(agc$mean_ba,2), round(agc$sd_ba,2), sep = " $\\pm$ "),
                round(agc$mean_ba,2))

tb <- data.frame(type = agc$type,
                 agc = mn_agc,
                 sd = mn_sd,
                 ba = mn_ba,
                 n = agc$n)

tb %>%
  kable(
    caption="Summary statistics for different forest plot types. We report the mean and standard deviation for Above Ground Carbon (AGC), basal area, stem density values and number of plots (as mentioned in Appendix Table 1).",
    booktabs = TRUE,
    escape = FALSE,
     col.names = c("forest type",
                   "AGC (Mg C $ha\\textsuperscript{-1}$)",
                   "stem density ($ha\\textsuperscript{-1}$)",
                   "basal area ($m\\textsuperscript{2}$ $ha\\textsuperscript{-1}$)",
                   "nr. plots"
                   )
    ) %>%
  kable_styling(latex_options = c("hold_position"))
```

### 2020-02-06 manuscript/appendix.tex
AGC uncertainty + manuscript tweaks

\caption{\label{tab:unnamed-chunk-1}Site description of all the current permanent sampling plots in the greater Yangambi region. We list the forest type, plot number, geographic location (in decimal degrees), stem density, basal area Above Ground Carbon (AGC), species richness and Land-Use and Land-Cover Change (LULCC) classes in a radius of 100m around each plot location.}
\centering
\begin{tabular}[t]{lrrrrrrrl}
\toprule
type & nr & latitude & longitude & stem density ($ha\textsuperscript{-1}$) & basal area ($m\textsuperscript{2}$ $ha\textsuperscript{-1}$) & AGC (Mg C $ha\textsuperscript{-1}$) & species richness & LULCC class coverage (\%)\\
\midrule
fallow & 1 & 0.7959139 & 24.49423 & 350 & 5.39000 & 6.7000 & 26 & 37 (1), 63 (3)\\
fallow & 2 & 0.7921028 & 24.49717 & 132 & 2.06000 & 2.0400 & 22 & 68 (1), 32 (3)\\
young-regrowth & 1 & 0.7894028 & 24.51755 & 322 & 20.44000 & 46.5600 & 40 & 68 (1), 32 (3)\\
young-regrowth & 2 & 0.7948806 & 24.49193 & 447 & 16.63000 & 27.8300 & 25 & 56 (1), 44 (3)\\
young-regrowth & 3 & 0.7931083 & 24.49013 & 313 & 17.80000 & 37.1000 & 43 & 51 (1), 49 (3)\\
\addlinespace
old-regrowth & 1 & 0.8824444 & 24.49614 & 384 & 19.48000 & 81.7800 & 92 & 100 (1)\\
mixed & 1 & 0.8135486 & 24.51264 & 563 & 34.81000 & 168.0400 & 83 & 100 (1)\\
mixed & 2 & 0.7805000 & 24.52109 & 403 & 35.25000 & 174.5800 & 78 & 100 (1)\\
mixed & 3 & 0.7866181 & 24.52349 & 367 & 30.69000 & 150.3000 & 75 & 100 (1)\\
mixed & 4 & 0.8140333 & 24.49370 & 432 & 33.01000 & 168.6100 & 84 & 100 (1)\\
\addlinespace
mixed & 5 & 0.8025611 & 24.48750 & 329 & 25.20000 & 124.1800 & 80 & 100 (1)\\
mixed & 6 & 0.9925556 & 24.53906 & 490 & 32.63000 & 203.8100 & 86 & 100 (1)\\
mixed & 7 & 0.9898056 & 24.53853 & 598 & 31.47000 & 146.1100 & 92 & 100 (1)\\
mixed & 8 & 0.9866111 & 24.53856 & 556 & 29.20000 & 148.2100 & 90 & 100 (1)\\
mono-dominant & 1 & 0.8269306 & 24.52303 & 344 & 31.80000 & 183.0100 & 48 & 100 (1)\\
\addlinespace
mono-dominant & 2 & 0.8282708 & 24.53196 & 436 & 32.06000 & 173.5800 & 55 & 100 (1)\\
mono-dominant & 3 & 0.7965903 & 24.49779 & 376 & 30.57000 & 166.4400 & 62 & 100 (1)\\
mono-dominant & 4 & 0.8080889 & 24.52811 & 374 & 27.69000 & 145.5500 & 46 & 100 (1)\\
mono-dominant & 5 & 0.8682806 & 24.45655 & 217 & 27.19000 & 159.0000 & 46 & 95 (1), 5 (2)\\
mono-dominant & 6 & 0.7992278 & 24.49195 & 378 & 33.95000 & 165.4800 & 68 & 100 (1)\\
\addlinespace
edge & 1 & 0.7895486 & 24.51990 & 415 & 30.93601 & 152.2792 & 77 & 100 (1)\\
edge & 2 & 0.7979472 & 24.48885 & 368 & 31.82097 & 152.1736 & 72 & 95 (1), 5 (3)\\
edge & 3 & 0.8144250 & 24.48555 & 458 & 35.79959 & 197.4022 & 86 & 100 (1)\\
edge & 4 & 0.7659306 & 24.51125 & 320 & 29.72547 & 154.6380 & 75 & 98 (1), 2 (3)\\
edge & 5 & 0.8691778 & 24.47019 & 459 & 33.72462 & 158.6934 & 88 & 100 (1)\\
\bottomrule
\end{tabular}
\end{table}

@@

\caption{\label{tab:unnamed-chunk-2}Flight path meta-data for the Isangi-Stanleyville aerial survey. Data provided consists of the flight path number, cardinal direction of the flight, the image numbers, and the duration of the flight provided by the start and end time of the acquisition. Data is sourced from Appendix Figure 2 and the sensor logs recorded in the margin of acquired images (see Figure 1 main manuscript).}
\centering
\begin{tabular}[t]{rllll}
\toprule
path & direction & image \# & start (H:M:S) & end (H:M:S)\\
\midrule
1 & W – E & 04 / 78 – 04 / 127 & 10:15:00 & 10:40:00\\
2 & W – E & 05 / 01 – 05 / 56 & 10:15:00 & 10:40:00\\
3 & W – E & 06 / 01 – 06 / 48 & 08:55:00 & 09:20:00\\
4 & W – E & 07 / 01 – 07 / 20 & 09:30:00 & 09:45:00\\
5 & W – E & 05 / 167 – 05 / 187 & 08:55:00 & 09:10:00\\
\addlinespace
6 & W – E & 07 / 67 – 07 / 82 & 10:50:00 & 11:00:00\\
7 & E – W & 06 / 49 – 06 / 95 & 09:35:00 & 10:05:00\\
8 & E – W & 05 / 57 – 05 / 103 & 10:20:00 & 10:50:00\\
9 & E – W & 04 / 128 – 04 / 176 & 10:50:00 & 11:10:00\\
10 & W – E & 08 / 01 – 08 / 27 & 09:05:00 & 09:20:00\\
\addlinespace
11 & W – E & 06 / 96 – 06 / 139 & 10:25:00 & 10:45:00\\
\bottomrule
\end{tabular}
\end{table}

@@

\caption{Overview of the complete flight plan of the survey around Kisangani (then Stanleyville) stored in the archives at the Africa Museum.}\label{fig:unnamed-chunk-3}
\end{figure}

@@

{\centering \includegraphics[width=82.67in,height=0.75\textheight]{./figures/flight_paths_meta_data}

@@

\caption{Overview of the complete flight plan meta-data as stored in the archives at the Africa Museum.}\label{fig:unnamed-chunk-4}
\end{figure}

@@

{\centering \includegraphics[width=14.39in,height=0.75\textheight]{./figures/archives_aerial_photos_2}

@@

\caption{Shelves with aerial survey images at the Africa Museum archives.}\label{fig:unnamed-chunk-5}
\end{figure}

{\centering \includegraphics[width=14.58in,height=0.5\textheight]{./figures/foto_bplot_psp}

\caption{Boxplots comparing the first principal component (PC1) of a site based FOTO analysis across different forest types for both contemporary (Geo-Eye) and historical orthomosaic data.}\label{fig:unnamed-chunk-6}
\end{figure}

>>>>

\caption{\label{tab:unnamed-chunk-1}Flight path meta-data for the Isangi-Stanleyville aerial survey. Data provided consists of the flight path number, cardinal direction of the flight, the image numbers, and the duration of the flight provided by the start and end time of the acquisition. Data is sourced from Appendix Figure 2 and the sensor logs recorded in the margin of acquired images (see Figure 1 main manuscript).}
\centering
\begin{tabular}[t]{rllll}
\toprule
path & direction & image \# & start (H:M:S) & end (H:M:S)\\
\midrule
1 & W – E & 04 / 78 – 04 / 127 & 10:15:00 & 10:40:00\\
2 & W – E & 05 / 01 – 05 / 56 & 10:15:00 & 10:40:00\\
3 & W – E & 06 / 01 – 06 / 48 & 08:55:00 & 09:20:00\\
4 & W – E & 07 / 01 – 07 / 20 & 09:30:00 & 09:45:00\\
5 & W – E & 05 / 167 – 05 / 187 & 08:55:00 & 09:10:00\\
\addlinespace
6 & W – E & 07 / 67 – 07 / 82 & 10:50:00 & 11:00:00\\
7 & E – W & 06 / 49 – 06 / 95 & 09:35:00 & 10:05:00\\
8 & E – W & 05 / 57 – 05 / 103 & 10:20:00 & 10:50:00\\
9 & E – W & 04 / 128 – 04 / 176 & 10:50:00 & 11:10:00\\
10 & W – E & 08 / 01 – 08 / 27 & 09:05:00 & 09:20:00\\
\addlinespace
11 & W – E & 06 / 96 – 06 / 139 & 10:25:00 & 10:45:00\\
\bottomrule
\end{tabular}
\end{table}

@@

\caption{\label{tab:unnamed-chunk-2}Site description of all the current permanent sampling plots in the greater Yangambi region. We list the forest type, plot number, geographic location (in decimal degrees), stem density, basal area Above Ground Carbon (AGC), species richness and Land-Use and Land-Cover Change (LULCC) classes in a radius of 100m around each plot location.}
\centering
\begin{tabular}[t]{lrrrrrrrl}
\toprule
type & nr & latitude & longitude & stem density ($ha\textsuperscript{-1}$) & basal area ($m\textsuperscript{2}$ $ha\textsuperscript{-1}$) & AGC (Mg C $ha\textsuperscript{-1}$) & species richness & LULCC class coverage (\%)\\
\midrule
fallow & 1 & 0.7959139 & 24.49423 & 350 & 5.39000 & 6.7000 & 26 & 37 (1), 63 (3)\\
fallow & 2 & 0.7921028 & 24.49717 & 132 & 2.06000 & 2.0400 & 22 & 68 (1), 32 (3)\\
young-regrowth & 1 & 0.7894028 & 24.51755 & 322 & 20.44000 & 46.5600 & 40 & 68 (1), 32 (3)\\
young-regrowth & 2 & 0.7948806 & 24.49193 & 447 & 16.63000 & 27.8300 & 25 & 56 (1), 44 (3)\\
young-regrowth & 3 & 0.7931083 & 24.49013 & 313 & 17.80000 & 37.1000 & 43 & 51 (1), 49 (3)\\
\addlinespace
old-regrowth & 1 & 0.8824444 & 24.49614 & 384 & 19.48000 & 81.7800 & 92 & 100 (1)\\
mixed & 1 & 0.8135486 & 24.51264 & 563 & 34.81000 & 168.0400 & 83 & 100 (1)\\
mixed & 2 & 0.7805000 & 24.52109 & 403 & 35.25000 & 174.5800 & 78 & 100 (1)\\
mixed & 3 & 0.7866181 & 24.52349 & 367 & 30.69000 & 150.3000 & 75 & 100 (1)\\
mixed & 4 & 0.8140333 & 24.49370 & 432 & 33.01000 & 168.6100 & 84 & 100 (1)\\
\addlinespace
mixed & 5 & 0.8025611 & 24.48750 & 329 & 25.20000 & 124.1800 & 80 & 100 (1)\\
mixed & 6 & 0.9925556 & 24.53906 & 490 & 32.63000 & 203.8100 & 86 & 100 (1)\\
mixed & 7 & 0.9898056 & 24.53853 & 598 & 31.47000 & 146.1100 & 92 & 100 (1)\\
mixed & 8 & 0.9866111 & 24.53856 & 556 & 29.20000 & 148.2100 & 90 & 100 (1)\\
mono-dominant & 1 & 0.8269306 & 24.52303 & 344 & 31.80000 & 183.0100 & 48 & 100 (1)\\
\addlinespace
mono-dominant & 2 & 0.8282708 & 24.53196 & 436 & 32.06000 & 173.5800 & 55 & 100 (1)\\
mono-dominant & 3 & 0.7965903 & 24.49779 & 376 & 30.57000 & 166.4400 & 62 & 100 (1)\\
mono-dominant & 4 & 0.8080889 & 24.52811 & 374 & 27.69000 & 145.5500 & 46 & 100 (1)\\
mono-dominant & 5 & 0.8682806 & 24.45655 & 217 & 27.19000 & 159.0000 & 46 & 95 (1), 5 (2)\\
mono-dominant & 6 & 0.7992278 & 24.49195 & 378 & 33.95000 & 165.4800 & 68 & 100 (1)\\
\addlinespace
edge & 1 & 0.7895486 & 24.51990 & 415 & 30.93601 & 152.2792 & 77 & 100 (1)\\
edge & 2 & 0.7979472 & 24.48885 & 368 & 31.82097 & 152.1736 & 72 & 95 (1), 5 (3)\\
edge & 3 & 0.8144250 & 24.48555 & 458 & 35.79959 & 197.4022 & 86 & 100 (1)\\
edge & 4 & 0.7659306 & 24.51125 & 320 & 29.72547 & 154.6380 & 75 & 98 (1), 2 (3)\\
edge & 5 & 0.8691778 & 24.47019 & 459 & 33.72462 & 158.6934 & 88 & 100 (1)\\
\bottomrule
\end{tabular}
\end{table}

\caption{\label{tab:unnamed-chunk-3}Summary statistics for different forest plot types. We report the mean and standard deviation for Above Ground Carbon (AGC), basal area, stem density values and number of plots (as mentioned in Appendix Table 1).}
\centering
\begin{tabular}[t]{llllr}
\toprule
forest type & AGC (Mg C $ha\textsuperscript{-1}$) & stem density ($ha\textsuperscript{-1}$) & basal area ($m\textsuperscript{2}$ $ha\textsuperscript{-1}$) & nr. plots\\
\midrule
edge & 163.04 $\pm$ 19.39 & 404 $\pm$ 60.03 & 32.4 $\pm$ 2.39 & 5\\
fallow & 4.37 $\pm$ 3.3 & 241 $\pm$ 154.15 & 3.72 $\pm$ 2.35 & 2\\
mixed & 160.48 $\pm$ 23.84 & 467.25 $\pm$ 99.42 & 31.53 $\pm$ 3.26 & 8\\
mono-dominant & 165.51 $\pm$ 12.75 & 354.17 $\pm$ 73.56 & 30.54 $\pm$ 2.64 & 6\\
old-regrowth & 81.78 & 384 & 19.48 & 1\\
\addlinespace
young-regrowth & 37.16 $\pm$ 9.37 & 360.67 $\pm$ 74.9 & 18.29 $\pm$ 1.95 & 3\\
\bottomrule
\end{tabular}
\end{table}

@@

\caption{Overview of the complete flight plan of the survey around Kisangani (then Stanleyville) stored in the archives at the Africa Museum.}\label{fig:unnamed-chunk-4}
\end{figure}

@@

{\centering \includegraphics[height=0.75\textheight]{./figures/flight_paths_meta_data}

@@

\caption{Overview of the complete flight plan meta-data as stored in the archives at the Africa Museum.}\label{fig:unnamed-chunk-5}
\end{figure}

@@

{\centering \includegraphics[height=0.75\textheight]{./figures/archives_aerial_photos_2}

@@

\caption{Shelves with aerial survey images at the Africa Museum archives, showing vasts amounts of historical data still mostly unexplored.}\label{fig:unnamed-chunk-6}
\end{figure}
